---
output:
  html_document:
    highlight: null
    css: style.css
    self_contained: no
    keep_md: true
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(stringr)

date <- "2/15/2018"
vendor <- "Pizza Capri"
title <- "Paper Title TBD"
file_title <- "Paper Title"
short_title_n = 2
speaker <- "Leslie Kay"
department <- "Professor, Department of Psychology and The College"
university <- "University of Chicago"
github_home <- "https://github.com/uchicago-computation-workshop"


```

```{r, echo=FALSE}
#Function to Shorten Title
small_title <- function(x, n=3) {
  ul <- unlist(strsplit(x, split = "\\s+"))[1:n]
  paste(ul,collapse=" ")
}

#Characters
unwanted_array = list(    'Š'='S', 'š'='s', 'Ž'='Z', 'ž'='z', 'À'='A', 'Á'='A', 'Â'='A', 'Ã'='A', 'Ä'='A', 'Å'='A', 'Æ'='A', 'Ç'='C', 'È'='E', 'É'='E',
                            'Ê'='E', 'Ë'='E', 'Ì'='I', 'Í'='I', 'Î'='I', 'Ï'='I', 'Ñ'='N', 'Ò'='O', 'Ó'='O', 'Ô'='O', 'Õ'='O', 'Ö'='O', 'Ø'='O', 'Ù'='U',
                            'Ú'='U', 'Û'='U', 'Ü'='U', 'Ý'='Y', 'Þ'='B', 'ß'='Ss', 'à'='a', 'á'='a', 'â'='a', 'ã'='a', 'ä'='a', 'å'='a', 'æ'='a', 'ç'='c',
                            'è'='e', 'é'='e', 'ê'='e', 'ë'='e', 'ì'='i', 'í'='i', 'î'='i', 'ï'='i', 'ð'='o', 'ñ'='n', 'ò'='o', 'ó'='o', 'ô'='o', 'õ'='o',
                            'ö'='o', 'ø'='o', 'ù'='u', 'ú'='u', 'û'='u', 'ý'='y', 'ý'='y', 'þ'='b', 'ÿ'='y' )


#Year
year <- substr(date, nchar(date)-4+1, nchar(date))

#Author Name
author_clean_lower <- str_replace_all(str_to_lower(speaker), " ", "_")

#Remove Unwanted Characters
out <- author_clean_lower
for(i in seq_along(unwanted_array))
    out <- gsub(names(unwanted_array)[i],unwanted_array[i],out)
author_clean <- out
author_lastname <- tail(strsplit(author_clean,split="_")[[1]],1)

#Repository Name
#repo = paste(year, author_clean, sep = "_")
repo = author_clean
issues_page <- paste(github_home, repo, "issues", sep="/")
repo_page <- paste(github_home, repo, sep="/")

#Create File Name Parts
short_title <- small_title(file_title, short_title_n)
paper_file <- paste(year, author_lastname, short_title, sep="  ")

#Clean Up File Name
punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'

#Remove Punctuation
lowered_name <- str_to_lower(paper_file)
stripped_name <- str_replace_all(lowered_name, punct, "")
cleaned_name <- str_replace_all(stripped_name, " ", "_")
cleaned_paper_file <- paste(cleaned_name, "pdf", sep=".")

#File Name Link
paper_link = paste(github_home, repo, "blob/master", cleaned_paper_file, sep="/"  )


#Clean Short Title
short_title_clean <- str_replace_all(short_title, punct, "")

```

<br>

<h3 class=pfblock-header> The Computational Social Science Workshop Presents </h3>

<h1 class=pfblock-header3> `r speaker` </h1>
<h3 class=pfblock-header3> `r department` </h3>
<h3 class=pfblock-header3> `r university` </h3>

<br><br>



<p class=pfblock-header3>The <a href="https://macss.uchicago.edu/content/computation-workshop"> Computational Social Science Workshop </a> at the University of Chicago cordially invites you to attend this week's talk:</p>

<br>

<div class=pfblock-header3>
<h2 class=pfblock-header>
  <a href="`r paper_link`" >`r title`</a>
</h2>

<br>
</div>

<p class=footertext2>

**Abstract:** TBD
</p>

<br>

<h4 class=pfblock-header3> Thursday, `r date` </h4>
<h4 class=pfblock-header3> 11:00am-12:20pm </h4>
<h4 class=pfblock-header3> Kent 120 </h4>

<br>

<p class=pfblock-header3>A light lunch will be provided by `r vendor`.</p>

<br><br>

<p class=footertext2>

**Dr. Kay** received a BA in Liberal Arts from St. John's College in Santa Fe, New Mexico and then worked for the original GenBank project at Los Alamos National Laboratory from 1982-85. She worked as a programmer/analyst in business applications for a number of years in the mid- to late 80s, and then returned to graduate school at UC Berkeley. She completed her dissertation research in the laboratory of Walter J. Freeman, and received a Ph.D. in Biophysics in 1995. Kay completed postdoctoral research in the laboratory of Gilles Laurent at the California Institute of Technology, where she studied olfactory bulb mitral cell responses to changes in odor context.

The Kay laboratory uses behavioral neurophysiology to examine how context, perceptual history, learning and physiological state interact within the brain during sensory perception. The lab studies the physiology of sensory and perceptual processing and learning in the olfactory and limbic systems, using laboratory rats and mice, with several behavioral paradigms designed to uncover different behavioral and cognitive states. Recording and analytical techniques span several scales, from the single neuron, to small populations, large populations, and distributed systems of cortical and subcortical regions. Theoretical interpretations are aimed at understanding system level dynamics and pathology and at examining neural coding hypotheses using the framework of complex dynamical systems.
</p>




<br><br>

---

<p class=footertext> The 2017-2018 <a href="https://macss.uchicago.edu/content/computation-workshop"> Computational Social Science Workshop </a> meets each Thursday from 11 a.m. to 12:20 p.m. in Kent 120. All interested faculty and graduate students are welcome.</p>

<p class=footertext>Students in the Masters of Computational Social Science program are expected to attend and join the discussion by posting a comment on the <a href="`r issues_page`"> issues page </a> of the <a href="`r repo_page`"> workshop's public repository on GitHub.</a> Further instructions are documented in the Computational Social Science Workshop's <a href="https://github.com/uchicago-computation-workshop/README"> README on Github.</a></p>
